# Part 1 - Obtaining Player Positions

Player positions grabbed from FBREF within `soccerdata` are overly broad, and would damage future analyses. It appears that the `worldfootballR` package in R is the best way to access data from **Transfermarkt**, which contains transfer-specific data that I will need soon, as well as more specific player positions.

```{r}
library(worldfootballR)
```

I'll explore several functions and see which one is mosst suitable for my purposes.

```{r}
pl_team_urls = tm_league_team_urls(country_name = "England", start_year = 2024)
pl_team_urls
```

```{r}
squad_stats = tm_squad_stats(pl_team_urls)
squad_stats
```

```{r}
# unique positions
unique(squad_stats$player_pos)
```

Not all positions are consistent here. Looks like Second Striker, Left Midfield, Right Midfield, and Attack are outlying.

```{r}

for (pos in unique(squad_stats$player_pos)) {
  print(pos)
  print(nrow(squad_stats[squad_stats$player_pos == pos,]))
}
```

```{r}
squad_stats[squad_stats$player_pos == "Second Striker",]
```

```{r}
write.csv(squad_stats, "PL2425_player_stats.csv")
```

